### 2018-08-30 manuscript.tex
Update manuscript.tex

There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We were not able to use newer dataset from those countries due to the lack of FGC benefits modules (checked in 09/17).

\_\_{[}CF: none of the countries had GPS data.  Kenya 2014, Mali 2012-3 and Nigeria 2013 have no value set {]}.  Sierra Leone 2013 does.  Should we use Sierra Leone 2008 or 2013? 2008 data is closer to the other data in terms of time period. It seems more convincing to if the data is all in a similar time span.  On the other hand, it is a much recent data and provides a more updated view{]}.

We included all the women despite of their FGC status and with or without daughters in the future model because our main interest was to study women's attitudes towards FGC continuance in general and their opinions counted as community attitudes towards this practice.  In the daughters model, we included only women with uncircumcised daughters because we were interested in mother's intention of whether to cut their daughters; and that resulted in xxx, xxx, xxx and xxx in the future model, and xxx, xxx, xxx and xxx in the daughter model respectively.

@@

The main constrcuts of analyzing FGC practice in this study were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}. (to confirm and update) The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, media use and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

@@

>>>>

There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules (checked in 09/17).

Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.

@@

The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm and update). The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, media use and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

@@

In the results of association of cutting daughter and mother's fgc status, the individual model and the community model were consistent; the effect of fgc prevalence among mothers, attitudes of fgc benefits and education were clear at the community level but not wealth, gender awareness and media consumption were not clear at the community level (meaning media use, gender awareness and education were less homogeneous?)

In the results of association of fgc future and mother's fgc status,
